### 2015-04-15 contract-language.tex
Added explanation for EC contract.

%  The above contract mandates that an effect $a$ must be visible to the current
%effect $\cureff$ if some effect $b$ that causally succeeds $a$ is also visible
%to $\cureff$. Thus, if every store replica always maintains and exposes a
%causal cut of updates to the client, then such a store will satisfy this
%contract. In such a system, an eventually consistent operation, such as
%\rcf{deposit}, can be satisfied as long as some replica is reachable.

@@

  \vspace{-1mm}
  \begin{cmathpar}
  \scc = \forall a.~\sameobj{a}{\cureff} \Rightarrow \vis{a}{\cureff} ~\vee~ \vis{\cureff}{a} ~\vee~ a = \cureff
  \end{cmathpar}
\end{itemize}

>>>>

  The above contract mandates that an effect $a$ must be visible to the current
  effect $\cureff$ if some effect $b$ that causally succeeds $a$ is also visible
  to $\cureff$. Thus, if every store replica always maintains and exposes a
  causal cut of updates to the client, then such a store will satisfy this
  contract. In such a system, an eventually consistent operation, such as
  \rcf{deposit}, which requires weaker guarantees than offered by the store, can
  be satisfied as long as some replica is reachable.

@@

  \vspace{-1mm}
  \begin{cmathpar}
  \scc = \forall a.~\sameobj{a}{\cureff} \Rightarrow \vis{a}{\cureff} ~\vee~ \vis{\cureff}{a} ~\vee~ a = \cureff
  \end{cmathpar}

\end{itemize}
